null_model

### 2020-09-18 analysis/calc_fd.Rmd
Add null values to fd_table and calculate SES, make sure plot names are being read correctly and years are appropriately labeled to null output.

  species_mat <- data %>%
    select(year, id, weight) %>%
    arrange(year) %>%
    arrange(id) %>%
    pivot_wider(names_from = id, values_from = weight, values_fill = 0) %>%
    select(-year)

  years <- data %>% 
    select(year) %>%
    distinct() %>%
    arrange(year)

@@

  fd_out <- as_tibble(dbFD_joggle(trait_mat, species_mat, w.abun = TRUE, ...))[,1:8] %>%
    cbind(years, .) %>%
    mutate(plot_id = unlist(filter_plot), trait_count = dim(trait_mat)[2])
    write_tsv(fd_out, paste0(here::here("data"), "/fd_output/", filter_plot, "_fd.tsv"))

@@

  future::plan("multiprocess", workers = 4)
  fd <- future_map(group_plots$plot_id, get_fd_safe, obs_data = group_data) %>%
    rbind()

@@

#fd <- map(1:num_groups, get_parallel_FD, df = data)
```

@@

Format tables
```{r}
fd_table <- fd_data %>% 
  select(year, plot_id, richness = nbsp, everything(), -sing.sp) %>%
  gather(metric, value, contains("F"), RaoQ) %>%
  left_join(biotime_traits %>% 
              select(plot_id, study_id, plot) %>%
                       distinct())

>>>>

  species_mat <- data %>%
    select(year, id, weight) %>%
    arrange(id) %>%
    pivot_wider(names_from = id, values_from = weight, values_fill = 0)

  years <- select(species_mat, year)

@@

  fd_out <- as_tibble(dbFD_joggle(trait_mat, select(species_mat, -year), w.abun = TRUE, ...))[,1:8] %>%
    cbind(years, .) %>%
    mutate(plot_id = unlist(filter_plot), trait_count = dim(trait_mat)[2])
    write_tsv(fd_out, paste0(here::here("data"), "/fd_output/", filter_plot, "_fd.tsv"))

@@

  future::plan("multiprocess", workers = 4)
  fd <- future_map(group_plots$plot_id, get_fd_safe, obs_data = group_data, 
                   m = "min", corr = "cailliez") %>%
    rbind()

@@

fd <- map(1:num_groups, get_parallel_FD, df = data)
```

@@

Format FD table with null values
```{r}
null_table <- pins::pin_get("null-table", board = "github")

fd_table <- fd_data %>% 
  select(year, plot_id, richness = nbsp, everything(), -sing.sp) %>%
  gather(metric, value, contains("F"), RaoQ) %>%
  left_join(biotime_traits %>% 
              select(plot_id, study_id, plot) %>%
                       distinct()) %>%
  left_join(null_table %>%
              select(plot_id, year, richness, metric, mean, sd), 
            by = c("year", "plot_id", "richness", "metric")) %>%
  mutate(SES = (value - mean)/sd)

### 2020-09-18 analysis/ts_null_model.Rmd
Add null values to fd_table and calculate SES, make sure plot names are being read correctly and years are appropriately labeled to null output.

  plot_samples <- read_csv(file_path) %>% mutate(plot_id = as.character(plot_id)) %>% replace(is.na(.), 0)

@@

  setwd(here::here())
  write_tsv(sample_fd, paste0(save_dir, "/null", unique(plot_samples$plot_id), ".csv"))

@@

Create Null table
```{r}
path <- here::here("data", "fd_null_output")
null_files <-  dir(path, "*.csv") %>%
  paste0(path, "/", .)

process_nulls <- function(file_path){
  data <- read_tsv(file_path) %>%
    mutate(plot_id = as.character(plot_id)) %>%
    select(year, plot_id, richness = nbsp, everything(), -sing.sp, -starts_with("CWM"), -n) %>%
    group_by(year)

@@

plan(multiprocess)
null_table <- future_map_dfr(null_files, process_nulls)

>>>>

  plot_samples <- read_csv(file_path, col_types = cols(plot_id = "c")) %>% mutate(plot_id = as.character(plot_id)) %>% replace(is.na(.), 0)

@@

  setwd(here::here())
  write_tsv(sample_fd, paste0(save_dir, "/null", unique(plot_samples$plot_id), ".tsv"))

@@

Create Null table
```{r}
path <- here::here("data", "fd_null_output")
null_files <-  dir(path, "*.tsv") %>%
  paste0(path, "/", .)

process_nulls <- function(file_path, n){
  data <- read_tsv(file_path, col_types = cols(plot_id = "c")) %>%
    select(year, plot_id, richness = nbsp, everything(), -sing.sp, -starts_with("CWM"), -n) %>%
    group_by(year)

@@

plan(multiprocess)
null_table <- future_map_dfr(null_files, process_nulls, n = n)
